Global Climate and Atmosphere Composition of the Ultra-Hot Jupiter WASP-103\lowercase{b} from \HST\ and Spitzer Phase Curve Observations

### 2018-01-03 ms.tex
clean up retrieval section

\author{Laura Kreidberg}
\affiliation{Harvard Society of Fellows\
78 Mt. Auburn St.\\
Cambridge, MA 02138, USA}
\affiliation{Harvard-Smithsonian Center for Astrophysics\
60 Garden St.\\
Cambridge, MA 02138}
\nocollaboration

\author{Vivien Parmentier}
\affiliation{Department of Planetary Sciences and Lunar and Planetary Laboratory, The University of Arizona}
\nocollaboration

\author{Michael R. Line}
\affiliation{Arizona State University}
\nocollaboration

\author{Kevin B. Stevenson}
\affiliation{Space Telescope Science Institute}
\nocollaboration

\author{Tom Louden}
\affiliation{University of Warwick}
\nocollaboration

\author{Mick\"{a}el Bonnefoy}
\affiliation{Universit\'{e} Grenoble Alpes}
\nocollaboration

\author{Jacqueline K. Faherty}
\affiliation{American Museum of Natural History}
\nocollaboration

\author{Gregory L. Henry}
\affiliation{Center of Excellence in Information Systems, Tennessee State University}
\nocollaboration

\author{Keivan Stassun}
\affiliation{Vanderbilt University}
\nocollaboration

\author{Jacob L. Bean}
\affiliation{University of Chicago}
\nocollaboration

\author{Jonathan Fortney}
\affiliation{University of California Santa Cruz}
\nocollaboration

\author{Adam Showman}
\affiliation{Department of Planetary Sciences and Lunar and Planetary Laboratory, The University of Arizona}
\nocollaboration

@@

\begin{deluxetable*}{lllllllllll}
	\tablecolumns{11}
	\tablewidth{0pt}:
	\tablecaption{Phase-Resolved Emission Spectra \label{table:spectra}}
	\tablehead{
	\colhead{$\lambda$} & \colhead{Dilution} & \colhead{$\phi = 0.1$} & \colhead{$\phi = 0.2$} & \colhead{$\phi = 0.3$} & \colhead{$\phi = 0.4$} & \colhead{$\phi = 0.5$} & \colhead{$\phi = 0.6$} & \colhead{$\phi = 0.7$} & \colhead{$\phi = 0.8$} & \colhead{$\phi = 0.9$}}
		\startdata
		1.175 & 0.10 & $ 179 \pm 79 $ & $ 411 \pm 77 $ & $ 647 \pm 80 $ & $ 1143 \pm 65 $ & $ 1259 \pm 47 $ & $ 1063 \pm 64 $ & $ 710 \pm 73 $ & $ 412 \pm 78 $ & $ 177 \pm 79 $ \\ 
		1.225 & 0.11 & $ 188 \pm 76 $ & $ 398 \pm 74 $ & $ 928 \pm 77 $ & $ 1276 \pm 62 $ & $ 1448 \pm 46 $ & $ 1216 \pm 62 $ & $ 888 \pm 71 $ & $ 539 \pm 75 $ & $ 280 \pm 76 $ \\ 
		1.275 & 0.11 & $ 166 \pm 76 $ & $ 379 \pm 74 $ & $ 869 \pm 77 $ & $ 1323 \pm 62 $ & $ 1480 \pm 46 $ & $ 1282 \pm 62 $ & $ 814 \pm 71 $ & $ 515 \pm 75 $ & $ 247 \pm 76 $ \\ 
		1.325 & 0.11 & $ 266 \pm 75 $ & $ 432 \pm 73 $ & $ 904 \pm 76 $ & $ 1357 \pm 62 $ & $ 1498 \pm 45 $ & $ 1267 \pm 61 $ & $ 925 \pm 70 $ & $ 552 \pm 74 $ & $ 333 \pm 75 $ \\ 
		1.375 & 0.12 & $ 189 \pm 81 $ & $ 514 \pm 78 $ & $ 928 \pm 82 $ & $ 1376 \pm 66 $ & $ 1611 \pm 48 $ & $ 1411 \pm 65 $ & $ 954 \pm 75 $ & $ 461 \pm 79 $ & $ 292 \pm 81 $ \\ 
		1.425 & 0.13 & $ 238 \pm 79 $ & $ 532 \pm 76 $ & $ 1198 \pm 79 $ & $ 1431 \pm 64 $ & $ 1718 \pm 47 $ & $ 1511 \pm 64 $ & $ 1063 \pm 73 $ & $ 605 \pm 77 $ & $ 338 \pm 79 $ \\ 
		1.475 & 0.14 & $ 191 \pm 81 $ & $ 527 \pm 79 $ & $ 1068 \pm 82 $ & $ 1460 \pm 66 $ & $ 1667 \pm 48 $ & $ 1392 \pm 66 $ & $ 1090 \pm 75 $ & $ 580 \pm 80 $ & $ 268 \pm 81 $ \\ 
		1.525 & 0.14 & $ 143 \pm 84 $ & $ 478 \pm 81 $ & $ 1048 \pm 85 $ & $ 1429 \pm 69 $ & $ 1623 \pm 50 $ & $ 1367 \pm 68 $ & $ 943 \pm 77 $ & $ 607 \pm 82 $ & $ 291 \pm 84 $ \\ 
		1.575 & 0.15 & $ 367 \pm 88 $ & $ 761 \pm 85 $ & $ 1088 \pm 89 $ & $ 1581 \pm 72 $ & $ 1749 \pm 52 $ & $ 1503 \pm 71 $ & $ 1107 \pm 81 $ & $ 754 \pm 86 $ & $ 422 \pm 88 $ \\ 
		1.625 & 0.16 & $ 359 \pm 93 $ & $ 565 \pm 90 $ & $ 1169 \pm 94 $ & $ 1590 \pm 76 $ & $ 1843 \pm 56 $ & $ 1593 \pm 75 $ & $ 1142 \pm 86 $ & $ 542 \pm 91 $ & $ 351 \pm 93 $ \\ 
		3.6 & 0.17 & $ 1148 \pm 333 $ & $ 3633 \pm 330 $ & $ 4487 \pm 320 $ & $ 4107 \pm 314 $ & $ 4458 \pm 383 $ & $ 3495 \pm 315 $ & $ 3720 \pm 330 $ & $ 2102 \pm 331 $ & $ 1431 \pm 334 $ \\ 
		4.5 & 0.16 & $ 1586 \pm 220 $ & $ 3468 \pm 214 $ & $ 4188 \pm 190 $ & $ 5334 \pm 179 $ & $ 5686 \pm 138 $ & $ 4904 \pm 183 $ & $ 3626 \pm 214 $ & $ 2575 \pm 217 $ & $ 1057 \pm 221 $ \\ 
		\enddata
		\vspace{-0.8cm}
		\tablecomments{comments}
	\end{deluxetable*}

@@

\subsection{Comparison with Previous Observations}
Cartier, Delrez.

@@

\subsection{Blackbody Fits}
A blackbody is the simplest model for the planet's thermal emission and provide a useful first evaluation of the atmospheric properties. The best fit blackbodies are shown in Figures \ref{fig:spectra} and \ref{fig:dayside}. This model performs well for some orbital phases, with $\chi^2_\nu$ ranging from 0.9 to 1.1 for phases $\phi = 0.1, 0.7$ and $0.8$. At other phases the blackbody model is a poorer fit, particularly to the \Spitzer\ data. For phases $0.2 - 0.6$, the \Spitzer\ eclipse depths are larger than predicted for the best fit blackbody, suggesting the presence of an emission feature. On the nightside (phase $0.9$), the \Spitzer\ $4.5\,\mu$m eclipse depth is \emph{smaller} than predicted, suggesting an absorption feature. These differences suggest changing thermal structure with longitude in the atmosphere.

We also fit blackbody models to the WFC3 data only, and found that they provide a good fit at all orbital phases. The $\chi^2_\nu$ values range from 0.5 to 1.6, with a median of 0.9. The best fit effective temperatures range from 1920 Kelvin on the nightside to 2980 Kelvin on the dayside. We report the best fit temperatures with uncertainties in Table\,\ref{table:teffs}.  The dayside spectrum is the poorest fit by the blackbody model. This finding is not a surprise because the dayside has higher signal-to-noise than the other orbital phases, thanks to the two secondary eclipse observations from \cite{cartier17}. The more sophisticated grid-based retrieval provides a better fit to the dayside.

@@

\subsection{Grid-Based Retrieval}
Since the phase-resolved spectra do not show spectrally resolved molecular features, we opted for a simple grid-based fit to the planet's atmospheric properties, similar to the grid search used in Mansfield et al. and Arcangeli et al. (in prep). We generated a grid from one-dimensional forward models of the atmosphere over a broad range of metallicities, carbon-to-oxygen ratios (C/O), and stellar irradiation. The stellar spectrum is scaled in intensity over the grid to model the unknown heat redistribution for the planet; i.e., a lower dayside irradiation is equivalent to more efficient heat transport to the nightside.

At each point in the grid, we compute forward models to determine self-consistent, radiative-convective temperature-pressure (T-P) profiles. We determine the molecular abundances in each atmospheric layer assuming thermochemical equilibrium.  We include opacity from the major absorbers expected for a hot Jupiter atmosphere, including H$_2$O, CO, CO$_2$, TiO, and VO (\textbf{Mike: what others?}). Notably, in contrast to many previous studies of the hottest planets, we also included opacity from H-, which is expected because water dissociates at dayside photospheric temperature and pressure (3000 K, 0.1 bar).  Using these opacities and T-P profiles, we calculated thermal emission spectra over the full grid using the CHIMERA retrieval suite.  We then explored the grid with an MCMC chain using the \texttt{emcee} package \citep{foremanmackey13}, and interpolated in the grid to calculate the likelihood at each model step. We fit this model to the dayside and nightside emission spectra (phases $\phi = 0.5$ and $0.1$).

\begin{figure}
\includegraphics[width = 0.5\textwidth]{Figures/WASP-103b_grid_DAYSIDE_stair_pairs_02.pdf}
\caption{Posterior distributions for WASP-103b's atmospheric heat redistribution, metallicity, and C/O, from a grid-based fit to the dayside emission spectrum. The histograms on the diagonal show the marginalized distribution of each parameter, with dashed lines indicating the median and surrounding 68\% confidence interval. \textbf{Mike: what percentiles does the colored shading correspond to?} The blue lines correspond to solar metallicity (1) and C/O (0.54).}
\label{fig:composition}
\end{figure}

\subsubsection{Dayside Spectrum}
The main characteristics of the dayside emission spectrum are: (1) it is blackbody-like at WFC3 wavelengths, and (2) in the \Spitzer\ bands, the planet-to-star flux is significantly higher than predicted for the best fit blackbody, indicating an emission feature.  The best fit spectrum reproduces these data fairly well, with $\chi^2_\nu$ = 1.77. The WFC3 and Spitzer $3.6\,\mu$m points are fit better ($\chi^2_\nu$  = 1.17 for these data alone), but the $4.5\,\mu$m point is higher than the best fit model by $2.9\,\sigma$.  The best fit model has a moderately enhanced metallicity ($23\times$ solar), carbon-to-oxygen equal to 0.76, poor heat redistribution, and a thermal inversion (temperature increasing with altitude).

Figure\,\ref{fig:opacities} shows the opacity contributions of key absorbers for the best fit.  In the optical (which we do not observe directly), there is strong absorption by TiO/VO.  In the near-infrared, the dominant absorbers are H$_2$O and H-.  The observed spectrum is featureless at these wavelengths, due to a combination of factors: water is partially dissociated in the photosphere, leading to a drop in abundance of FIXME.  It also produces H- opacity (single H atoms bind with free electrons), which dominates spectral features from H$_2$O at wavelengths shorter than FIXME $\mu$m.  Water is also an efficient coolant, so lower water abundance leads to a more isothermal photosphere and weakens the features even more.  Taken together, all these factors conspire to produce a nearly featureless spectrum from $1.1 - 1.7\,\mu$m. Finally, in the infrared the dominant absorber is CO, which produces the emission feature at \Spitzer\ wavelengths.

\begin{figure}
\includegraphics[width = 0.5\textwidth]{Figures/xsec_FULL.pdf}
\caption{Opacities.}
\label{fig:opacities}
\end{figure}

\subsubsection{Dayside Spectrum}

The TiO/VO absorption heats the upper atmosphere, resulting in a thermal inversion. Figure\,\ref{fig:TP} shows a selection of 100 randomly selected dayside T-P profiles. The profiles are nearly isothermal over a pressure range of $1-10^{-2}$ bars, with a median temperature near 2900 Kelvin. The temperature increases over $10^{-2} - 10^{-3}$ bars to 3500 Kelvin, and then begins to decrease again at pressures below $10^{-3}$ bar. (\textbf{Mike: what are the contribution functions?}).

@@

We infer a heat redistribution $f = 0.4^{+0.03}_{-0.02}$. The $f$ parameter is allowed to range from 0 (isotropic heat distribution) to 0.5 (dayside emission only). Our estimate of $f$ is close to the maximum, indicating inefficient transport of heat to the nightside. Poor heat transport is observed in other very hot planets as well, due to damping of heat-propagating waves by fast radiative cooling or frictional drag in a partially ionized atmosphere \citep{komacek16}. The heat redistribution is correlated with atmospheric metallicity (\textbf{Mike: why is this?}).

@@

\begin{figure}
\includegraphics[width = 0.5\textwidth]{Figures/TP.pdf}
\caption{Dayside temperature-pressure profiles from the grid retrieval (red lines) compared to the profile from the substellar point for the FIXME GCM.}
\label{fig:TP}
\end{figure}

@@

\acknowledgments
We thank a lot of people. Caroline Morley, Thomas Beatty, Ming Zhao, Kim Star Cartier, Hannah Diamond-Lowe, Nick Cowan (make him a coauthor?)

>>>>

\author{Laura Kreidberg}
\affiliation{Harvard Society of Fellows\
78 Mt. Auburn St.\\
Cambridge, MA 02138, USA}
\affiliation{Harvard-Smithsonian Center for Astrophysics\
60 Garden St.\\
Cambridge, MA 02138}

\author{Vivien Parmentier}
\affiliation{Department of Planetary Sciences and Lunar and Planetary Laboratory, The University of Arizona}

\author{Michael R. Line}
\affiliation{Arizona State University}

\author{Kevin B. Stevenson}
\affiliation{Space Telescope Science Institute}

\author{Tom Louden}
\affiliation{University of Warwick}

\author{Mick\"{a}el Bonnefoy}
\affiliation{Universit\'{e} Grenoble Alpes}

\author{Jacqueline K. Faherty}
\affiliation{American Museum of Natural History}

\author{Gregory L. Henry}
\affiliation{Center of Excellence in Information Systems, Tennessee State University}

\author{Keivan Stassun}
\affiliation{Vanderbilt University}

\author{Jacob L. Bean}
\affiliation{University of Chicago}

\author{Jonathan Fortney}
\affiliation{University of California Santa Cruz}

\author{Adam Showman}
\affiliation{Department of Planetary Sciences and Lunar and Planetary Laboratory, The University of Arizona}

@@

\begin{deluxetable*}{lllllllllll}
	\tablecolumns{11}
	\tablewidth{0pt}
	\tablecaption{Phase-Resolved Emission Spectra \label{table:spectra}}
	\tablehead{
	\colhead{$\lambda$} & \colhead{Dilution} & \colhead{$\phi = 0.1$} & \colhead{$\phi = 0.2$} & \colhead{$\phi = 0.3$} & \colhead{$\phi = 0.4$} & \colhead{$\phi = 0.5$} & \colhead{$\phi = 0.6$} & \colhead{$\phi = 0.7$} & \colhead{$\phi = 0.8$} & \colhead{$\phi = 0.9$}}
		\startdata
		1.175 & 0.10 & $ 179 \pm 79 $ & $ 411 \pm 77 $ & $ 647 \pm 80 $ & $ 1143 \pm 65 $ & $ 1259 \pm 47 $ & $ 1063 \pm 64 $ & $ 710 \pm 73 $ & $ 412 \pm 78 $ & $ 177 \pm 79 $ \\ 
		1.225 & 0.11 & $ 188 \pm 76 $ & $ 398 \pm 74 $ & $ 928 \pm 77 $ & $ 1276 \pm 62 $ & $ 1448 \pm 46 $ & $ 1216 \pm 62 $ & $ 888 \pm 71 $ & $ 539 \pm 75 $ & $ 280 \pm 76 $ \\ 
		1.275 & 0.11 & $ 166 \pm 76 $ & $ 379 \pm 74 $ & $ 869 \pm 77 $ & $ 1323 \pm 62 $ & $ 1480 \pm 46 $ & $ 1282 \pm 62 $ & $ 814 \pm 71 $ & $ 515 \pm 75 $ & $ 247 \pm 76 $ \\ 
		1.325 & 0.11 & $ 266 \pm 75 $ & $ 432 \pm 73 $ & $ 904 \pm 76 $ & $ 1357 \pm 62 $ & $ 1498 \pm 45 $ & $ 1267 \pm 61 $ & $ 925 \pm 70 $ & $ 552 \pm 74 $ & $ 333 \pm 75 $ \\ 
		1.375 & 0.12 & $ 189 \pm 81 $ & $ 514 \pm 78 $ & $ 928 \pm 82 $ & $ 1376 \pm 66 $ & $ 1611 \pm 48 $ & $ 1411 \pm 65 $ & $ 954 \pm 75 $ & $ 461 \pm 79 $ & $ 292 \pm 81 $ \\ 
		1.425 & 0.13 & $ 238 \pm 79 $ & $ 532 \pm 76 $ & $ 1198 \pm 79 $ & $ 1431 \pm 64 $ & $ 1718 \pm 47 $ & $ 1511 \pm 64 $ & $ 1063 \pm 73 $ & $ 605 \pm 77 $ & $ 338 \pm 79 $ \\ 
		1.475 & 0.14 & $ 191 \pm 81 $ & $ 527 \pm 79 $ & $ 1068 \pm 82 $ & $ 1460 \pm 66 $ & $ 1667 \pm 48 $ & $ 1392 \pm 66 $ & $ 1090 \pm 75 $ & $ 580 \pm 80 $ & $ 268 \pm 81 $ \\ 
		1.525 & 0.14 & $ 143 \pm 84 $ & $ 478 \pm 81 $ & $ 1048 \pm 85 $ & $ 1429 \pm 69 $ & $ 1623 \pm 50 $ & $ 1367 \pm 68 $ & $ 943 \pm 77 $ & $ 607 \pm 82 $ & $ 291 \pm 84 $ \\ 
		1.575 & 0.15 & $ 367 \pm 88 $ & $ 761 \pm 85 $ & $ 1088 \pm 89 $ & $ 1581 \pm 72 $ & $ 1749 \pm 52 $ & $ 1503 \pm 71 $ & $ 1107 \pm 81 $ & $ 754 \pm 86 $ & $ 422 \pm 88 $ \\ 
		1.625 & 0.16 & $ 359 \pm 93 $ & $ 565 \pm 90 $ & $ 1169 \pm 94 $ & $ 1590 \pm 76 $ & $ 1843 \pm 56 $ & $ 1593 \pm 75 $ & $ 1142 \pm 86 $ & $ 542 \pm 91 $ & $ 351 \pm 93 $ \\ 
		3.6 & 0.17 & $ 1148 \pm 333 $ & $ 3633 \pm 330 $ & $ 4487 \pm 320 $ & $ 4107 \pm 314 $ & $ 4458 \pm 383 $ & $ 3495 \pm 315 $ & $ 3720 \pm 330 $ & $ 2102 \pm 331 $ & $ 1431 \pm 334 $ \\ 
		4.5 & 0.16 & $ 1586 \pm 220 $ & $ 3468 \pm 214 $ & $ 4188 \pm 190 $ & $ 5334 \pm 179 $ & $ 5686 \pm 138 $ & $ 4904 \pm 183 $ & $ 3626 \pm 214 $ & $ 2575 \pm 217 $ & $ 1057 \pm 221 $ \\ 
		\enddata
		\vspace{-0.8cm}
		\tablecomments{comments}
	\end{deluxetable*}

@@

\subsection{Comparison with Previous Observations}
We compared our results to the dayside emission spectrum reported by \cite{cartier17}, which is based on a Gaussian process analysis of two secondary eclipses from \HST/WFC3. The shape of their spectrum is consistent with what we find, but their eclipse depths are 125 ppm smaller on average. In their analysis, \cite{cartier17} noted that the Gaussian process fit produces smaller eclipse depths than a parametric fit (also by 125 ppm). One explanation for this difference is that the Gaussian process models some of the astrophysical signal. If the planet's thermal phase variation is absorbed into the instrument systematic model, the measured eclipse depths would be lower by about 100 ppm. Since our analysis accounts for the thermal phase variation, it is more likely to provide a robust estimate of the secondary eclipse depths.  Our estimated uncertainties are a factor of four smaller than those reported in \cite{cartier17}, which is consistent with photon-limited expectations (our data set includes two additional eclipses, a factor of five longer out-of-eclipse baseline, and has 60\% larger wavelength bins).

We also compared our dayside spectrum to the $z'$ and $K_\mathrm{S}$-band secondary eclipse depths reported in \cite{delrez18}. The $z'$ eclipse is $1.0\,\sigma$ lower than our best fit blackbody spectrum (described in \S\,\ref{sec:composition}), and the $K_\mathrm{S}$ measurement is higher than the model by $2.5\,\sigma$. Since these results are consistent with (but less precise than) the WFC3 data, we do not include them in our analysis of the atmospheric composition, but we encourage additional measurements in the $K_\mathrm{S}$ band to confidently determine whether an emission feature is present at those wavelengths.

@@

\subsection{Blackbody Fits}
A blackbody is the simplest model for the planet's thermal emission and provide a useful first evaluation of the atmospheric properties. The best fit blackbodies are shown in Figures \ref{fig:spectra} and \ref{fig:dayside}. This model performs well for some orbital phases, with $\chi^2_\nu$ ranging from 0.9 to 1.1 for phases $\phi = 0.1, 0.7$ and $0.8$. At other phases the blackbody model is a poorer fit, particularly to the \Spitzer\ data. For phases $0.2 - 0.6$, the \Spitzer\ eclipse depths are significantly larger than predicted for the best fit blackbody, suggesting the presence of an emission feature. On the nightside (phase $0.9$), the \Spitzer\ $4.5\,\mu$m eclipse depth is \emph{smaller} than predicted, suggesting an absorption feature. These differences indicate changes in thermal structure with longitude in the atmosphere.

We also fit blackbody models to the WFC3 data only, and found that they provide a good fit at all orbital phases. The $\chi^2_\nu$ values range from 0.5 to 1.6, with a median of 0.9. The best fit effective temperatures range from 1920 Kelvin on the nightside to 2980 Kelvin on the dayside. We report the best fit temperatures with uncertainties in Table\,\ref{table:teffs}.  The dayside spectrum is the poorest fit by the blackbody model. This finding is not a surprise because the dayside has higher signal-to-noise than the other orbital phases, thanks to the two secondary eclipse observations from \cite{cartier17}. The more sophisticated grid-based retrieval (described in the next section) provides a better fit to the dayside.

@@

\subsection{Grid-Based Retrieval}
Since the phase-resolved spectra do not show spectrally resolved molecular features, we opted for a simple grid-based fit to the planet's atmospheric properties, similar to the grid search used in \cite{arcangeli18, mansfield18}. We generated a grid from one-dimensional forward models of the atmosphere over a broad range of metallicities, carbon-to-oxygen ratios (C/O), and stellar irradiation. The stellar spectrum is scaled in intensity over the grid to model the unknown heat redistribution for the planet; i.e., a lower dayside irradiation is equivalent to more efficient heat transport to the nightside.

At each point in the grid, we compute forward models to determine self-consistent, radiative-convective temperature-pressure (T-P) profiles. (\textbf{Mike: citations?}) We determine the molecular abundances in each atmospheric layer assuming thermochemical equilibrium \citep[calculated with the NASA CEA routine;][]{gordon94}.  We include opacity from the major absorbers expected for a hot Jupiter atmosphere, including H$_2$O, CO, CO$_2$, TiO, VO, FeH, and H$_2$-H$_2$ CIA. Notably, in contrast to many previous studies of the hottest planets, we also included opacity from H-, which is an important absorber at temperatures above 2500 K \citep{arcangeli18}.  Using these opacities and T-P profiles, we calculated thermal emission spectra over the full grid using the CHIMERA retrieval suite \citep[described in][]{line13a, line14}.  We then explored the grid with an MCMC chain using the \texttt{emcee} package \citep{foremanmackey13} and interpolated in the grid to calculate the likelihood at each model step. We fit this model to the dayside and nightside emission spectra (phases $\phi = 0.5$ and $0.1$).

\begin{figure}
\includegraphics[width = 0.5\textwidth]{Figures/WASP-103b_grid_DAYSIDE_stair_pairs_02.pdf}
\caption{Posterior distributions for WASP-103b's atmospheric heat redistribution, metallicity, and C/O, from a grid-based fit to the dayside emission spectrum. The histograms on the diagonal show the marginalized distribution of each parameter, with dashed lines indicating the median and surrounding 68\% credible interval. The blue lines correspond to solar metallicity (1) and C/O (0.54). The 2D histograms mark the 1, 2, and 3$\,\sigma$ credible regions in dark, medium, and light blue, respectively.}
\label{fig:composition}
\end{figure}

\subsubsection{Dayside Spectrum}
The main characteristics of the dayside emission spectrum are: (1) it is blackbody-like at WFC3 wavelengths, and (2) in the \Spitzer\ bands, the planet-to-star flux is significantly higher than predicted for the best fit blackbody, indicating an emission feature.  The best fit spectrum reproduces these data fairly well, with $\chi^2_\nu$ = 1.77. The largest contribution to the $\chi^2$ value is the $4.5\,\mu$m eclipse depth, which is larger than the best fit model prediction by $2.9\,\sigma$. When the $4.5\,\mu$m point is removed, the fit has $\chi^2_\nu = 1.17$.  The best fit model has a moderately enhanced metallicity ($23\times$ solar), carbon-to-oxygen equal to 0.76, poor heat redistribution, and a thermal inversion (temperature increasing with altitude).

Figure\,\ref{fig:opacities} shows the opacity contributions of key absorbers for the best fit.  In the optical (which we do not observe directly), there is strong absorption by TiO, VO, and FeH.  In the near-infrared, the H$_2$O, H-, and hydrides/oxides all contribute to the opacity, leading to nearly constant opacity over the WFC3 wavelength range.  In cooler atmospheres, water is the dominant absorber over this bandpass, but in WASP-103b, H$_2$O is partially dissociated in the photosphere, leading to a drop in abundance by a factor of $\sim10$ (see Figure\,\ref{fig:summary}). Water also has intrinsically weaker features at high temperature \citep{tinetti12}. Finally, water is an efficient coolant, so lower water abundance leads to a more isothermal photosphere, which further weakens the contrast in and out of the water band in the observed spectrum. On top of this, there is significant H- opacity from single H atoms bound with free electrons, which fills in the opacity at wavelengths shorter than $1.5\,\mu$m.  Taken together, all these factors conspire to produce a nearly featureless spectrum from $1.1 - 1.7\,\mu$m. Finally, in the infrared the dominant absorber is CO, which produces the emission feature at \Spitzer\ wavelengths.

\begin{figure}
\includegraphics[width = 0.5\textwidth]{Figures/xsec_FULL.pdf}
\caption{Abundance weighted absorption cross-sections illustrating the important opacity sources at the photospheric pressure level (5 mbar). The strong CO feature at 4.5\,$\mu$m contributes to the high planet-to-star flux at that wavelength.  Water, hydrides/oxides, and the H- bound-free opacities all play a role in shaping the \HST/WFC3 spectrum.}
\label{fig:opacities}
\end{figure}

Figure\,\ref{fig:summary} shows a summary of the temperature-pressure profile and abundances for the best fit model. The T-P profile is inverted, with temperature increasing from 2800 to 3500 K over the pressure range $10^{-2} - 10^{-3}$ bar.  The  thermal inversion is driven by absorption of optical light by oxides and hydrides in the upper atmosphere.  The contribution functions FIXME
%Figure\,\ref{fig:TP} shows a selection of 100 randomly selected dayside T-P profiles. The profiles are nearly isothermal over a pressure range of $1-10^{-2}$ bars, with a median temperature near 2900 Kelvin. The temperature increases over $10^{-2} - 10^{-3}$ bars to 3500 Kelvin, and then begins to decrease again at pressures below $10^{-3}$ bar.

@@

We infer a heat redistribution $f = 0.4^{+0.03}_{-0.02}$. The $f$ parameter is allowed to range from 0 (isotropic heat distribution) to 0.5 (dayside emission only). Our estimate of $f$ is close to the maximum, indicating inefficient transport of heat to the nightside. Poor heat transport is observed in other very hot planets as well, due to damping of heat-propagating waves by fast radiative cooling or frictional drag in a partially ionized atmosphere \citep{komacek16}. The heat redistribution is correlated with atmospheric metallicity because increasing metallicity pushes the photosphere to higher, cooler pressure levels (\textbf{Mike: does this make sense, since the atmosphere has a thermal inversion?}).

@@

\begin{figure}
\includegraphics[width = 0.5\textwidth]{Figures/atmosphere_summary.pdf}
\caption{Summary of the 1D self-consistent model atmosphere fits.  The temperature-pressure profile (top axis) is indicated by the 1-sigma spread of 500 randomly drawn T-P profiles from the posterior (light red) and a representative fit, with $f$=0.4, [M/H]=1.5, and C/O=0.7 (dark red).  The normalized thermal emission contribution functions for the \Spitzer\ points are shown in solid red, the WFC3 in-water band ($1.33-1.48\,\mu$m) in dark blue, and WFC3 out-of-water-band in light blue.  The observations probe between $\sim0.01$ and 0.001 bar, just above the tropopause region of the atmosphere where the temperature is increasing.  The dashed curves are thermochemical equilibrium mixing ratios for important absorbers computed along the representative fit's self-consistent T-P profile.  Note the rapid dissociation of water above the $\sim10$ mbar level where the inversion begins.}
\label{fig:summary}
\end{figure}

@@

\acknowledgments
Some of the data presented in this paper were obtained from the Mikulski Archive for Space Telescopes (MAST). STScI is operated by the Association of Universities for Research in Astronomy, Inc., under NASA contract NAS5-26555. Support for MAST for non-HST data is provided by the NASA Office of Space Science via grant NNX13AC07G and by other grants and contracts. This work also made use of the Python packages  SciPy and NumPy \citep{jones_scipy_2001, van2011numpy}. The authors are grateful for helpful conversations with Caroline Morley, Thomas Beatty, Ming Zhao, Kim Star Cartier, Hannah Diamond-Lowe, and Nick Cowan. We also thank the organizers of the 2016 Santa Cruz Kavli Summer Program and the 2017 Ringberg Atmospheres of Disks and Planets meeting for facilitating many discussions and collaborations.
